\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-12-08 doc/USER_MANUAL/manual_SPECFEM3D.tex
added ref to PuAmKa09 about DG for fault rupture dynamics

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06,WiStBuGh10}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,Arn82,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,AiMoMu06,BeLaPi06,DuKa06,DeSeWh08,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions.
In particular, it can accurately handle very distorted mesh elements \citep{OlSe11}.
Note that in most geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies)
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient;
conforming mesh doubling bricks can efficiently handle mesh size variations \citep{KoTr02a,KoLiTrSuStSh04}.\\

>>>>

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06,WiStBuGh10}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,Arn82,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,AiMoMu06,BeLaPi06,DuKa06,DeSeWh08,PuAmKa09,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions.
In particular, it can accurately handle very distorted mesh elements \citep{OlSe11}.
Note that in most geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies, in which very high frequencies need to be modeled near the fault, see e.g. \cite{PuAmKa09})
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient;
conforming mesh doubling bricks can efficiently handle mesh size variations \citep{KoTr02a,KoLiTrSuStSh04}.\\
